s.function

### 2023-02-21 src/s_la_per_firm.Rmd
lads

- speed, other metrics? 
- understand rsquare
- model LAs
- add SE for the line plots [link](https://stackoverflow.com/questions/26020142/adding-shade-to-r-lineplot-denotes-standard-error)

@@

df <- df %>% left_join(firms) %>% 
  mutate(n_by_firm = (n*1000)/firms) %>% # '000 websites/firm
  #filter(!is.na(firms)) %>% 
  select(-n, -firms) %>% 
  rename(n = n_by_firm)

@@

```{r}
df.country <- df %>% group_by(year) %>% 
  summarise(n = sum(n, na.rm = T))

@@

path.out <- paste0(path, "/outputs/s_uk.png")

df.country %>% 
  ggplot(aes(x = year, y = n) ) +
  geom_point() +
  geom_line(aes(y = prednls), size = 1) +
  scale_x_continuous("year", labels = as.character(df.country$year), breaks = df.country$year) +
  geom_vline(xintercept = 2003) +
  ylab("N. of websites") +
  ggtitle("S-curve, UK") +
  theme(plot.title = element_text(hjust = 0.5))

@@

@@

# plots
path.out <- paste0(path, "/outputs/per_firm/lad_")

for (i in all.la){
p <- ggplot(pred %>% left_join(a.la) %>% 
              filter(ladcd == i), aes(x = year, y = n, color = fast) ) +
  geom_point() +
  geom_line(aes(y = prednls), size = 1) +
  scale_x_continuous("year", labels = as.character(df$year), breaks = df$year) +
  geom_vline(xintercept = pred %>% left_join(a.la) %>% filter(ladcd == i) %>% dplyr::select(estimate) %>% first()) +
  ylab("N. of websites") + 
  labs(color = "Website \ndiffusion speed") +
  labs(title = paste0(la@data %>% filter(LAD21CD== i) %>% dplyr::select(LAD21NM) %>% first(), ", ", i)) +
  theme(legend.position=c(.9,.15)) +
  scale_color_manual(values = c("fast" = "purple",
                                "slow"="orange")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_vline(xintercept = 2003, colour="grey30", linetype="dashed")

ggsave(p, filename = paste(path.out, i, ".png", sep = ""))

>>>>

- speed, other metrics? 
- understand rsquare
- model LAs
- ~~add SE for the line plots~~ [link](https://stackoverflow.com/questions/26020142/adding-shade-to-r-lineplot-denotes-standard-error). No as we have the points in the plots, so SE is not needed

@@

df <- df %>% left_join(firms) %>% 
  mutate(n_by_firm = n/firms) %>% # N websites/firm
  #filter(!is.na(firms)) %>% 
  select(-n, -firms) %>% 
  rename(n = n_by_firm)

@@

```{r}
df.country <- df %>% group_by(year) %>% 
  summarise(n = mean(n, na.rm = T))

@@

path.out <- paste0(path, "/outputs/s_uk_per_firm.png")

df.country %>% 
  ggplot(aes(x = year, y = n) ) +
  geom_point() +
  geom_line(aes(y = prednls), size = 1) +
  scale_x_continuous("year", labels = as.character(df.country$year), breaks = df.country$year) +
  geom_vline(xintercept = 2003) +
  ylab("N. of websites / per firm") +
  ggtitle("S-curve, UK") +
  theme(plot.title = element_text(hjust = 0.5))

@@

```{r}
a.la <- as_tibble()
all.la <- df %>% filter(ladcd != "NA") %>% distinct(ladcd) %>% 
  #top_n(n=2) %>% 
  simplify2array()
simplify2array(all.la)

@@

# plots
path.out <- paste0(path, "/outputs/s_lad_per_firm/lad_")

for (i in all.la){

  xmid_la <- pred %>% left_join(a.la) %>% filter(ladcd == i) %>% dplyr::select(estimate) %>% first()
  lines <- data.frame(
    intercepts = c(2003, xmid_la[1]),
    Xmid = c("UK", i)
  )

p <- ggplot(pred %>% left_join(a.la) %>% 
              filter(ladcd == i), aes(x = year, y = n, color = fast) ) +
  geom_point() +
  geom_line(aes(y = prednls), size = 1) +
  scale_x_continuous("year", labels = as.character(df$year), breaks = df$year) +
  #geom_vline(xintercept = pred %>% left_join(a.la) %>% filter(ladcd == i) %>% dplyr::select(estimate) %>% first()) +
  ylab("N. of websites / per firm") + 
  labs(color = "Website \ndiffusion speed") +
  labs(title = paste0(la@data %>% filter(LAD21CD== i) %>% dplyr::select(LAD21NM) %>% first(), ", ", i)) +
  theme(legend.position=c(.9,.15)) +
  scale_color_manual(values = c("fast" = "purple",
                                "slow"="orange"),
                     limits = force) +
  geom_vline(
    data=lines,
    aes(xintercept = intercepts, linetype=Xmid),
    size=.5, key_glyph='path', colour="grey30"
    ) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) #+
  #geom_vline(xintercept = 2003, colour="grey30", linetype="dashed")

ggsave(p, filename = paste(path.out, i, ".png", sep = ""), bg="white")
